Transactional Memory Concurrency Verification with Landslide

### 2018-03-13 htm/paper.tex
state the data race theorem

\begin{theorem}[Transactions are a Global Lock]
	asdfasdfaf
\end{theorem}

\begin{proof}
	asdfasdf
\end{proof}

>>>>

Let $\tiiat{\mu},\tjjat{\nu}$ be a pair of memory accesses to the same address, at least one a write,
in some transactional execution $I$ normalized under Lemma~\ref{lem:equiv}.
Then let $\mathsf{lockify}_m(\tkkat{L})$ denote a function over instructions in $I$,
which replaces $\tkkat{L}$ with $\tkkat{\mathsf{lock}(m)}$ if $L$ is a successful HTM begin,
with a no-op if $L$ is a transaction abort,
or with $\tkkat{\mathsf{unlock}(m)}$ if $L$ is an HTM end,
or no replacement otherwise.
Finally, let $I' = \exists m. \mathsf{lockify}_m(I)$,
the execution with all successful transactions replaced by an abstract global lock.
Lemma~\ref{lem:equiv} guarantees mutual exclusion of $m$.

\begin{theorem}[Transactions are a Global Lock]
	$\tiiat{\mu},\tjjat{\nu}$ is a data race in $I$ iff it is a data race in $I'$.
\end{theorem}

\begin{proof}
We prove one case for each variant definiton for data races \cite{quicksand}.

\begin{itemize}
	\item {\bf Limited Happens-Before.}
	\item {\bf Pure Happens-Before.}
\end{itemize}

\end{proof}
